---
title: "Econ HW 4"
author: "Madeline Berger"
date: "5/30/2019"
output: html_document
---

###Homework 4

```{r, echo = FALSE }
library(tidyverse)
library(ggplot2)
library(stargazer)
library(ggpubr)
library(knitr)


abatement <- read.csv("HW4Data.csv")

```



Notes: 
Current carbon emissions in the sectors are: 
- (A=180, B=200, C=220, and D=300).
- Sectors A, B, and C are in country X. Sector D is in a different country, Y.
- Prices are in $/ton and quantities are in tons.


Your task is to produce a 1 page memo, with supporting appendices, to advise country X (and in some questions, country Y) about how best to reduce carbon emissions. Your memo and appendices must address the following questions. 

### Exploration for A and assignment of values 
```{r}

MCA_plot <- ggplot (abatement, aes(x = Abatement, y = MC_A)) +
  geom_line()

MCA_plot

degree_1A <- lm(abatement$MC_A ~ abatement$Abatement)

summary(degree_1A)

A_y_int <- degree_1A$coefficients[1]
A_coeff <- degree_1A$coefficients[2]
```

### Exploration for B, C and D 
```{r}

MCB_plot <- ggplot (abatement, aes(x = Abatement, y = MC_B)) +
  geom_line()

MCB_plot

########## B ##################

degree_1B <- lm(abatement$MC_B ~ abatement$Abatement)

summary(degree_1B)

B_y_int <- degree_1B$coefficients[1]
B_coeff <- degree_1B$coefficients[2]

########### C ##############

degree_1C <- lm(abatement$MC_C ~ abatement$Abatement)

summary(degree_1C)

C_y_int <- degree_1C$coefficients[1]
C_coeff <- degree_1C$coefficients[2]

########### D ##############

degree_1D <- lm(abatement$MC_D ~ abatement$Abatement)

summary(degree_1D)

D_y_int <- degree_1D$coefficients[1]
D_coeff <- degree_1D$coefficients[2]

#degree_2 <- lm(abatement$MC_B ~ abatement$Abatement + I(abatement$Abatement^2))

#summary(degree_2)

#degree_3 <- lm(abatement$MC_B ~ abatement$Abatement + I(abatement$Abatement^2) + I(abatement$Abatement^3))

#summary(degree_3)

#degree_4 <- lm(abatement$MC_B ~ abatement$Abatement + I(abatement$Abatement^2) + I(abatement$Abatement^3) + I(abatement$Abatement^4))

#summary(degree_4)

#degree_5 <- lm(abatement$MC_B ~ abatement$Abatement + I(abatement$Abatement^2) + I(abatement$Abatement^3) + I(abatement$Abatement^4) + I(abatement$Abatement^5))

#summary(degree_5)

#degree_6 <- lm(abatement$MC_B ~ abatement$Abatement + I(abatement$Abatement^2) + I(abatement$Abatement^3) + I(abatement$Abatement^4) + I(abatement$Abatement^5)  + I(abatement$Abatement^6))

#summary(degree_6)

#degree_7 <- lm(abatement$MC_B ~ abatement$Abatement + I(abatement$Abatement^2) + I(abatement$Abatement^3) + I(abatement$Abatement^4) + I(abatement$Abatement^5)  + I(abatement$Abatement^6)+ I(abatement$Abatement^7))

#summary(degree_7)



```


###1.
Write down a plausible functional form for the marginal cost of abatement for sector A. Use regression analysis to estimate the parameters of that function. Repeating this for sectors B, C, and D will give you a model of the marginal cost of abatement function for each sector. How well do your models fit the data for each sector? You may need to experiment with different functional forms. Produce a plot of the estimated marginal abatement cost functions in all four sectors (this plot should go in your memo).

```{r}

#assuming the need to abate all the pollution

A_sup <- function(q){
  A_y_int + A_coeff*q
}

B_sup <-function(q){
  B_y_int + B_coeff*q
}

C_sup <-function(q){
  C_y_int + C_coeff*q
}

D_sup <-function(q){
  D_y_int + D_coeff*q
}


abate_plot <- ggplot(data.frame(x=c(0,200)), aes(x=x)) + 
    stat_function(fun=A_sup, geom ="line", aes(color = "A")) + 
    stat_function(fun=B_sup, geom ="line", aes(color = "B")) +
    stat_function(fun=C_sup, geom ="line", aes(color = "C")) +
    stat_function(fun=D_sup, geom ="line", aes(color = "D"))+
    labs(x = "Abatement", y = "Price")+
    scale_x_continuous(limits =c(0,110), expand = c(0,0))+
    scale_y_continuous(limits=c(-15,50), expand=c(0,0))+
    theme_bw()

abate_plot

```

###2. 
Using these models and the current level of carbon emissions, derive each sector’s demand curve for carbon emissions. In other words, how much would each sector be willing to pay for the right to pollute the first unit, second unit, etc? Draw these demand curves on a graph. Which sector is willing to pay the most for the first unit of carbon emissions?

```{r}

############ A ################
#Find demand curve for A
dem_y_A <- A_sup(180)

A_0 <- A_sup(0)

slope_A <- (A_0 - dem_y_A)/(180-0)

 #x intercept for demand curve should be found using y intercept of supply 


#demand curve as a function 
A_demand <- function(q){
  dem_y_A + slope_A*q
}


############ B #############

dem_y_B <- B_sup(200)

B_0 <- B_sup(0)

slope_B <- (B_0-dem_y_B)/(200-0)


#demand curve as a function 
B_demand <- function(q){
  dem_y_B + slope_B*q
}


########## C ##############

dem_y_C <- C_sup(220)

C_0 <- C_sup(0)

slope_C <- (C_0-dem_y_C)/(220-0)


#demand curve as a function 
C_demand <- function(q){
  dem_y_C + slope_C*q
}



########## D ################

dem_y_D <- D_sup(300)

D_0 <- D_sup(0)

slope_D <- (D_0-dem_y_D)/(300-0)


#demand curve as a function 
D_demand <- function(q){
  dem_y_D + slope_D*q
}




ggplot(data.frame(x=c(0,200)), aes(x=x)) + 
  stat_function(fun=A_demand, geom ="line", aes(color = "Demand A")) + 
  stat_function(fun=B_demand, geom ="line", aes(color = "Demand B")) +
  stat_function(fun=C_demand, geom ="line", aes(color = "Demand C")) +
  stat_function(fun=D_demand, geom ="line", aes(color = "Demand D")) +
  labs(x = "Emission", y = "Price")+
  scale_x_continuous(limits =c(0,400), expand = c(0,0))+
  scale_y_continuous(limits=c(0,200), expand=c(0,0))+
  theme_bw()



```


###3. 
3. Now focus on country X (which contains sectors A, B, and C). Assume there are no “co-benefits” from carbon abatement (i.e. that there are no local pollutants that are affected by carbon abatement). Suppose to meet the Paris Accord commitments, country X needs to cut all carbon emissions in half. For each of the policy options listed below, derive: (1) the total cost of meeting the target in country X, (2) the cost (or benefit) to each sector, and (3) the tax revenue generated.

a. Cap on carbon. Each sector (A, B, and C) must cut its carbon emissions by 100 tons (thus
reducing total emissions from 600 down to 300).
b. Tax on carbon. To emit a ton of carbon in country X, you must pay a tax of $t. You will need to find the tax that accomplishes the desired reduction.
c. Cap and trade. Each sector (A, B, C) is allocated carbon permits equal to their current emissionsminus 100 (same as in (a) above), thus achieving the total reduction of 300. Then, these three sectors are allowed to trade with each other. You will need to derive the outcome of that
trading.

```{r}
#aggregate horizontally

deno_ABC = A_coeff * B_coeff + A_coeff * C_coeff + B_coeff * C_coeff
agg_y_int_ABC = (A_y_int*B_coeff*C_coeff/deno_ABC) + (B_y_int*A_coeff*C_coeff/deno_ABC) + (C_y_int*B_coeff*A_coeff/deno_ABC)
agg_coeff_ABC = (A_coeff*B_coeff*C_coeff/deno_ABC)

agg_abate_ABC <- function(x){
  agg_coeff_ABC*x + agg_y_int_ABC
}

tax_price <- agg_abate_ABC(300)
unit_A <- (tax_price - A_y_int)/A_coeff #how much each sector pollutes with the 300 cap
unit_B <- (tax_price - B_y_int)/B_coeff
unit_C <- (tax_price - C_y_int)/C_coeff

agg_AC <- function(x){
  (A_coeff*C_coeff/(A_coeff+C_coeff)) * x + (A_y_int*C_coeff+C_y_int*A_coeff)/(A_coeff+C_coeff)
}

int_AC <- (A_y_int - C_y_int)/C_coeff

int_ABC <- (B_y_int - (A_y_int*C_coeff+C_y_int*A_coeff)/(A_coeff+C_coeff))/(A_coeff*C_coeff/(A_coeff+C_coeff))

agg_abate <- function(x){
  if(x<int_AC) {
    C_y_int + C_coeff*x
  } else if (x >= int_AC && x <= int_ABC) {
    (A_coeff*C_coeff/(A_coeff+C_coeff)) * x + (A_y_int*C_coeff+C_y_int*A_coeff)/(A_coeff+C_coeff)
  } else {
    agg_coeff_ABC*x + agg_y_int_ABC
  }
} #create piecewise function of agg demand

agg_abate <- Vectorize(agg_abate)

ggplot(data.frame(x=c(0,500)), aes(x=x)) + 
  stat_function(fun=A_sup, geom ="line", aes(color = "Abatement A"), size = 0.3) + 
  stat_function(fun=B_sup, geom ="line", aes(color = "Abatement B"), size = 0.3) +
  stat_function(fun=C_sup, geom ="line", aes(color = "Abatement C"), size = 0.3) +
  stat_function(fun=agg_abate, geom ="line", aes(color = "Aggregated"), size = 1.0)+
  labs(x = "Abatement", y = "Price ($/ton)")+
  scale_x_continuous(limits =c(0,400), expand = c(0,0))+
  scale_y_continuous(limits=c(-20,60), expand=c(0,0))+
  geom_hline(yintercept = tax_price, linetype = "dashed")+
  geom_vline(xintercept = 300, linetype = "dashed")+
  geom_vline(xintercept = unit_A, linetype = "dashed", size = 0.3)+
  geom_vline(xintercept = unit_B, linetype = "dashed", size = 0.3)+
  geom_vline(xintercept = unit_C, linetype = "dashed", size = 0.3)+
  scale_color_brewer("Abatement Curve", palette = "Dark2")+
  theme_pubr()


```



```{r}
#aggregate horizontally 

plot_x <- ggplot(data.frame(x=c(0,200)), aes(x=x)) + 
  stat_function(fun=A_demand, geom ="line", aes(color = "Demand A")) + 
  stat_function(fun=B_demand, geom ="line", aes(color = "Demand B")) +
  stat_function(fun=C_demand, geom ="line", aes(color = "Demand C")) +
  labs(x = "Abatement", y = "Price")+
  scale_x_continuous(limits =c(0,200), expand = c(0,0))+
  scale_y_continuous(limits=c(0,200), expand=c(0,0))+
  theme_bw()

plot_x
```
####a.
```{r}

#solve the cost for a,b,c cap for carbon

cost_cap_A_X <- integrate(A_sup, 0, 100)$value
cost_cap_B_X <- integrate(B_sup, 0, 100)$value
cost_cap_C_X <- integrate(C_sup, 0, 100)$value
cost_cap_total <- cost_cap_A_X + cost_cap_B_X + cost_cap_C_X

#no tax revenue generated

```

####b.
```{r}
#solve the benefit for a,b,c tax for carbon

cost_tax_A_X <- integrate(A_sup, 0, unit_A)$value
cost_tax_B_X <- integrate(B_sup, 0, unit_B)$value
cost_tax_C_X <- integrate(C_sup, 0, unit_C)$value
cost_tax_total <- cost_tax_A_X + cost_tax_B_X + cost_tax_C_X

tax_revenue_X <- 300*tax_price

```

####c.

```{r}

#solve for the benefit for a,b,c for cap and trade
#(A=180, B=200, C=220, and D=300)

A_trade <- (180-unit_A-80)
B_trade <- (200-unit_B-100)
C_trade <-(220-unit_C-120)

A_trans <- A_trade*tax_price #A buys this
B_trans <- B_trade*tax_price #B sells this 
C_trans <- C_trade*tax_price #C buys this 


```



###4. 
Again, without any co-benefits, suppose that country Y (which only has one carbon-emitting sector, D) has no obligation to reduce its emissions. Country X asks country Y to enter the country X carbon market. Doing so would require country Y to put a cap on carbon emissions at its current level of emissions (300 tons), but would then allow country Y to sell carbon offsets to sectors A, B, or C. Are there any incentives for country Y to enter country X’s carbon market and to thus place a voluntary cap on its emissions? Are there any incentives for country X to try to attract country Y into its market?

```{r}

price_lastunit_D <- D_sup(300)
#if this price is higher than the equilibrium from country X, country Y will purchase from country X

#cap and trade with y 




```



###5. 
Now assume that every ton of carbon emissions creates 1 ton of local air pollution. Local air pollution causes economic damages (health, environmental, etc.), but only in the country in which it is emitted. Assume there are no local air pollution regulations in either country X or country Y.

a. In a carbon cap and trade market that only covers sectors in country X, how much local air
pollution would you expect in country X? In country Y?
b. If country Y enters the carbon market for country X (as in question 4 above), how much local pollution will there be in country X and country Y?
c. What advice can you give country X and country Y about the desirability of allowing
international trade of carbon emissions credits?

```{r}

deno_ABCD <- A_coeff*B_coeff*C_coeff + D_coeff*B_coeff*C_coeff + A_coeff*D_coeff*C_coeff + A_coeff*B_coeff*D_coeff
agg_y_int_ABCD = (A_y_int*B_coeff*C_coeff*D_coeff/deno_ABCD) + (B_y_int*A_coeff*C_coeff*D_coeff/deno_ABCD) + (C_y_int*B_coeff*A_coeff*D_coeff/deno_ABCD) + (D_y_int*B_coeff*C_coeff*A_coeff/deno_ABCD)
agg_coeff_ABCD = (A_coeff*B_coeff*C_coeff*D_coeff/deno_ABCD)

agg_abate_ABCD <- function(x){
  agg_coeff_ABCD*x + agg_y_int_ABCD
}

tax_price_ABCD <- agg_abate_ABCD(600)
unit_A_XY <- (tax_price_ABCD - A_y_int)/A_coeff
unit_B_XY <- (tax_price_ABCD - B_y_int)/B_coeff
unit_C_XY <- (tax_price_ABCD - C_y_int)/C_coeff
unit_D_XY <- (tax_price_ABCD - D_y_int)/D_coeff

int_ABCD <- (D_y_int - agg_y_int_ABC)/agg_coeff_ABC

agg_abate_ABCD <- function(x){
  if(x<int_AC) {
    C_y_int + C_coeff*x
  } else if (x >= int_AC && x < int_ABC) {
    (A_coeff*C_coeff/(A_coeff+C_coeff)) * x + (A_y_int*C_coeff+C_y_int*A_coeff)/(A_coeff+C_coeff)
  } else if (x >= int_ABC && x < int_ABCD) {
    agg_coeff_ABC*x + agg_y_int_ABC
  } else {
    agg_coeff_ABCD*x + agg_y_int_ABCD
  }
}

agg_abate_ABCD <- Vectorize(agg_abate_ABCD)

ggplot(data.frame(x=c(0,500)), aes(x=x)) + 
  stat_function(fun=A_sup, geom ="line", aes(color = "Abatement A"), size = 0.3) + 
  stat_function(fun=B_sup, geom ="line", aes(color = "Abatement B"), size = 0.3) +
  stat_function(fun=C_sup, geom ="line", aes(color = "Abatement C"), size = 0.3) +
  stat_function(fun=D_sup, geom ="line", aes(color = "Abatement D"), size = 0.3) +
  stat_function(fun=agg_abate_ABCD, geom ="line", aes(color = "Aggregated"), size = 1.0)+
  labs(x = "Abatement", y = "Price ($/ton)")+
  scale_x_continuous(limits =c(0,800), expand = c(0,0))+
  scale_y_continuous(limits=c(-20,60), expand=c(0,0))+
  scale_color_brewer("Abatement", palette = "Dark2")+
  geom_hline(yintercept = tax_price_ABCD, linetype = "dashed")+
  geom_vline(xintercept = 600, linetype = "dashed")+
  geom_vline(xintercept = unit_A_XY, linetype = "dashed", size = 0.3)+
  geom_vline(xintercept = unit_B_XY, linetype = "dashed", size = 0.3)+
  geom_vline(xintercept = unit_C_XY, linetype = "dashed", size = 0.3)+
  geom_vline(xintercept = unit_D_XY, linetype = "dashed", size = 0.3)+
  theme_pubr()


```

####.a

```{r}

#a. In a carbon cap and trade market that only covers sectors in country X, how much local air pollution would you expect in country X? In country Y?

pol_x <- unit_A+unit_B+unit_C

pol_y <- 300

#b. If country Y enters the carbon market for country X (as in question 4 above), how much local pollution will there be in country X and country Y?



```

